---
title: "LIANA_EDA"
author: "David Smith"
date: "11/8/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
# Sys.setenv(PATH= paste("/home/smithd30/miniconda3/envs/cell2cell/bin",Sys.getenv()["PATH"],sep=":"))
Sys.setenv(RETICULATE_PYTHON = "/home/smithd30/miniconda3/envs/cell2cell/bin/python")
library(reticulate)
library(magrittr)
library(liana)
library(Seurat)
library(patchwork)
library(here)
```

```{r}
# load this outside of RMarkdown:
# load('/mnt/isilon/cscb/Projects/10x/pillaiv/SCTC-VP-22/vinodh-5-3-integration/processed/02-annotation/cellxgene_out_FILTERED_no4k_doublets.h5ad')

# load processed/02-annotation/final_integration.rds
#   NOTE--This version doesn't the combat adjusted counts
seu <- readRDS("/mnt/isilon/cscb/Projects/10x/pillaiv/SCTC-VP-22/vinodh-5-3-integration/processed/02-annotation/symphony_transfer_integrated_DGS_edited.RDS")



```

```{r}
# CD

Idents(seu) <- "disease"
DefaultAssay(seu) <- "RNA"

dat_test <- subset(seu, idents=c("HVCD","R","MCD"))
dat_test <- NormalizeData(dat_test)


```
```{r}
# alt-abundance test

sce <- as.SingleCellExperiment(dat_test)
sce %>%
  get_abundance_summary(sample_col = "edit.ident",
                        idents_col = "pred_anno", 
                        min_cells = 30, # min cells per sample
                        min_samples = 2, # min samples
                        min_prop = 0.2 # min prop of samples
                        ) %>%
  plot_abundance_summary()

```

Applying the filtering
```{r}
sce <- liana::filter_nonabundant_celltypes(sce,
                                           sample_col = "edit.ident",
                                           idents_col = "pred_anno")

```

Running LIANA with context awareness
https://saezlab.github.io/liana/articles/liana_cc2tensor.html

```{r}
sce <- liana_bysample(sce = sce,
                      sample_col = "edit.ident",
                      idents_col = "pred_anno",
                      method = "sca", # we use SingleCellSignalR's score alone
                      expr_prop = 0, # expression proportion threshold
                      inplace=TRUE, # saves inplace to sce
                      return_all = FALSE,# whether to return non-expressed interactions
                      parallelize = T, workers = 8
                      )
```

```{r}
sce <- liana_tensor_c2c(sce = sce,
                        score_col = 'LRscore',
                        rank = NULL,  # set to None to estimate for you data!
                        how='outer',  #  defines how the tensor is built
                        # conda_env = "cell2cell", # used to pass an existing conda env with cell2cell
                        use_available = TRUE # detect & load cell2cell if available
                        )
# unfortunately, the session crashed during the decompose step, but the factor selection finished with selecting 12 
sce <- liana_tensor_c2c(sce = sce,
                        score_col = 'LRscore',
                        rank = 12,  # set to None to estimate for you data!
                        how='outer',  #  defines how the tensor is built
                        conda_env = "cell2cell", # used to pass an existing conda env with cell2cell
                        use_available = FALSE, # detect & load cell2cell if available
                        )
# For use on GPU
sce <- liana_tensor_c2c(sce = sce,
                        score_col = 'LRscore',
                        rank = NULL,  # set to None to estimate for you data!
                        how='outer',  #  defines how the tensor is built
                        conda_env = "cell2cell", # used to pass an existing conda env with cell2cell
                        use_available = FALSE, # detect & load cell2cell if available
                        device = "cuda:0"
                        )
saveRDS(sce, "CD_cellFilter_RNA_checkpoint.RDS")
```

```{r}
sce <- readRDS("/mnt/isilon/cscb/Projects/10x/pillaiv/SCTC-VP-22/vinodh-5-3-integration/code/07-LIANA/CD_checkpoint.RDS")
factors <- get_c2c_factors(sce, group_col = "disease", sample_col = "edit.ident")

# random plots
plot_c2c_overview(sce, group_col="disease", sample_col="edit.ident")
all_facts_boxes <- plot_context_boxplot(sce,
                                        sample_col = "edit.ident",
                                        group_col = "disease",
                                        test="aov", # applicable only to two groups
                                        paired=FALSE #! Is this the case for your data?
                                        )
# there are redundant plots, drop every other
all_facts_boxes <- all_facts_boxes[seq(1, length(all_facts_boxes), 2)]

wrap_plots(
    all_facts_boxes,
    ncol=4) +
    plot_layout(guides = "collect") & theme(legend.position = 'bottom') +
    theme(plot.tag = element_text(face = 'bold', size = 16)
          )

plot_context_heat(sce, group_col = "disease", sample_col="edit.ident")

# Run this outside of markdown:
# pdf(
#   here("code/07-LIANA/outs/KFD/cell2cell/factor_cell_types.pdf"),
#   height = 8,
#   width = 11
# )
# 
# for(i in 1:9){
#   print(plot_c2c_cells(sce,
#                  factor_of_int = paste0("Factor.",as.character(i)),
#                  name = "Loadings \nProduct"))
# }
# 
# while (!is.null(dev.list()))  dev.off()

calculate_gini(factors$senders)
calculate_gini(factors$receivers)

plot_lr_heatmap(sce,  n = 5, cluster_columns=FALSE)
```

Testing enrichments
```{r}
progeny <- decoupleR::get_progeny(organism = 'human', top=5000) %>%
    select(-p_value)

# convert to LR sets
progeny_lr <- generate_lr_geneset(sce,
                                  resource = progeny)

mat <- factors$interactions %>%
    column_to_rownames("lr") %>%
  as.matrix()

# run enrichment analysis with decoupler
# (we fit a univariate linear model for each gene set)
# We don't consider genesets with minsize < 10
res <- decoupleR::run_ulm(mat = mat,
                          network = progeny_lr,
                          .source = "set",
                          .target = "lr",
                          minsize=10) %>%
  mutate(p_adj = p.adjust(p_value, method = "fdr"))

res %>% # sig/isnig flag
  mutate(significant = if_else(p_adj <= 0.05, "signif.", "not")) %>%
  ggplot(aes(x=source, y=condition, shape=significant,
             colour=score, size=-log10(p_value+1e-36))) +
  geom_point() +
  scale_colour_gradient2(high = "red", low="blue") +
  scale_size_continuous(range = c(3, 12)) +
  scale_shape_manual(values=c(21, 16)) +
  theme_bw(base_size = 15) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(x="Pathway",
       y="Factor",
       colour="Activity"
       )
```
Identifying driving interactions of enrichment
```{r}
lrs <-  factors$interactions %>%
  left_join(progeny_lr, by="lr") %>%
  filter(set=="NFkB") %>%
  select(lr, set, mor, loading = Factor.10) %>%
  mutate(lr = gsub(as.character(str_glue("\\^")), " -> ", lr)) %>%
  mutate(weight = if_else(mor >= 0, "positive", "negative"))
lrs %>%
  # only label those that are > x
  mutate(lr = if_else(loading>=0.001 & abs(mor) > 2, lr, "")) %>%
  ggplot(aes(x=mor, y=loading, colour=weight)) +
  # label only top 20
  stat_smooth(method = "lm", col = "red") +
  geom_point(alpha = 0.5) + 
  ggrepel::geom_label_repel(aes(label = lr)) +
  theme_bw(base_size = 15) +
  scale_colour_manual(values = c("royalblue3", "red")) +
  labs(x="Pathway Weight", y="LR Loading")
```


## Running individually
RUNNING LIANA
```{r}
# dat@assays$integrated <- NULL
KFD_res <- liana_wrap(dat, idents_col = "pred_anno", assay = "combat",
                      parallelize = T, workers = 6)
KFD_res <- KFD_res %>% liana_aggregate()
```

```{r}

VlnPlot(dat, features = "IFI44L", group.by = "cell_type", assay = 'SCT')


KFD_res %>%
  liana_dotplot(source_groups = c("Plasmacytoid dendritic cells"),
                target_groups = c("Cytotoxic CD8 T cells", "Macrophages"),
                ntop = 20)

p <- chord_freq(KFD_res,
                source_groups = c("Cytotoxic CD8 T cells", "Plasmacytoid dendritic cells", "Macrophages"),
                target_groups = c("Cytotoxic CD8 T cells", "Plasmacytoid dendritic cells", "Macrophages"))

KFD_res %>%
  liana_dotplot(source_groups = c("Macrophages"),
                target_groups = c("Cytotoxic CD8 T cells", "Stromal cells"),
                ntop = 20)

hvcd1_res_trunc <- hvcd1_res %>%
   # only keep interactions concordant between methods
  filter(aggregate_rank <= 0.05) # note that these pvals are already corrected

heat_freq(hvcd1_res_trunc)
```

Now testing the reactive data
```{r}

dat <- subset(dat_test, idents="R")

R_res <- liana_wrap(dat, idents_col = "pred_anno", assay = "combat",
                      parallelize = T, workers = 6)
R_res <- R_res %>% liana_aggregate()
```

Now, how to filter the interactions unique to KFD....

```{r}
# only keep interactions concordant between methods
KFD_res_trunc <- KFD_res %>% 
  filter(aggregate_rank <= 0.05)
heat_freq(KFD_res_trunc)
R_res_trunc <- R_res %>% 
  filter(aggregate_rank <= 0.05)
heat_freq(R_res_trunc)
# outer joins? Make an index of cell-type source-target?
#   make intersection of terms, filter on unique ones

KFD_res_trunc <- KFD_res_trunc %>% mutate(cc_itxn = paste(source, target, ligand.complex, receptor.complex, sep="."))
R_res_trunc <- R_res_trunc %>% mutate(cc_itxn = paste(source, target, ligand.complex, receptor.complex, sep="."))
cc_itxn_intersect <- intersect(KFD_res_trunc$cc_itxn, R_res_trunc$cc_itxn)
cc_itxn_union <- union(KFD_res_trunc$cc_itxn, R_res_trunc$cc_itxn)

KFD_res_trunc_filter <- KFD_res_trunc[!(KFD_res_trunc$cc_itxn %in% cc_itxn_intersect),]
R_res_trunc_filter <- R_res_trunc[!(R_res_trunc$cc_itxn %in% cc_itxn_intersect),]



```


Within the common interactions, is there a noticeable difference of interaction types.
Revise the plotting such that:
dot size = binned delta sca.LRscore 
dot color = normalized difference in NATMI score

```{r}
KFD_res_itersect <- mutate(KFD_res, cc_itxn = paste(source, target, ligand.complex, receptor.complex, sep=".")) %>%
  filter(cc_itxn %in% cc_itxn_union) %>%
  select(source, target, ligand.complex, receptor.complex, natmi.edge_specificity, sca.LRscore, cc_itxn, aggregate_rank)
R_res_itersect <-mutate(R_res, cc_itxn = paste(source, target, ligand.complex, receptor.complex, sep=".")) %>%
  filter(cc_itxn %in% cc_itxn_union) %>%
  select(source, target, ligand.complex, receptor.complex, natmi.edge_specificity, sca.LRscore, cc_itxn, aggregate_rank)

all_res <- merge(KFD_res_itersect, R_res_itersect, by = "cc_itxn", suffixes = c("KFD","R"), all.x = F, all.y = F)
all_res$dNATMI <- all_res$natmi.edge_specificityKFD - all_res$natmi.edge_specificityR
all_res$dLRscore <- all_res$sca.LRscoreKFD - all_res$sca.LRscoreR
all_res$d_rank <- -log(all_res$aggregate_rankKFD) - -log(all_res$aggregate_rankR)

```

